\cvsection{Experience}

\begin{cventries}

  \cventry
    {Staff Software Developer} % Job title
    {Kong} % Organization
    {Remote, Canada} % Location
    {2024 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented secure Single Sign-On (SSO) strategies for Kong's Konnect cloud platform, unlocking millions in enterprise ARR by enhancing authentication and access control.}
        \item {Actively mentored engineers, fostering growth in system design, security best practices, and platform scalability.}
        \item {Drove continuous improvement in engineering processes by promoting ownership of services, enhancing observability, and enforcing strict SLOs for reliability and performance of authentication, authorization, auditing and search services.}
      \end{cvitems}
    }

  \cventry
    {Director of Technology} % Job title
    {Ambassador Labs} % Organization
    {Remote, Canada} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trusted adviser and member of the leadership team, championing the company's vision through compelling storytelling and strategic positionning.}
        \item {Shaped both operational and technical roadmaps, fortifying our stature as a premier engineering organization.}
        \item {Transformed business objectives and product concepts into actionable stories and project blueprints for four engineering teams.}
        \item {Elevated our DevOps practices, achieving "Elite" status based on DORA metrics.}
      \end{cvitems}
    }

  \cventry
    {Principal \& Senior Principal Software Developer (Tech Lead)} % Job title
    {Ambassador Labs} % Organization
    {Remote, Canada} % Location
    {2020 - 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the software architecture for Ambassador's SaaS Platform and cloud infrastructure, emphasizing rapid business feature delivery and cost optimization.}
        \item {Mentored engineering tech leads, guiding them on growth opportunities, informed technical decision-making, prioritization, and development cycle strategy.}
        \item {Championed "operational excellence" initiatives by establishing an incident response process, automating infrastructure changes, enhancing monitoring, and introducing chaos engineering practices like Game Days.}
      \end{cvitems}
    }

  \cventry
    {Senior Software Developer} % Job title
    {Ambassador Labs (formerly Datawire.io)} % Organization
    {Remote, Canada} % Location
    {2019 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Open-source contributor and maintainer of the Emissary-ingress, Telepresence and Kubernetes SIG-network projects hosted by the CNCF.}
        \item {Developed proprietary features using Go and Python for the Ambassador platform, complemented by comprehensive documentation and articles to streamline user adoption.}
        \item {Collaborated with the Marketing team to implement rapid growth experiments and establish an advanced analytics pipeline for business metrics.}
      \end{cvitems}
    }

  \cventry
    {Senior Staff Software Developer (DevOps \& SRE Tech Lead)} % Job title
    {AppDirect} % Organization
    {Montréal, Canada} % Location
    {2018 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built observability in a micro-service architecture through tracing (OpenTracing, OpenCensus, Jaeger) and monitoring (Prometheus, Grafana).}
        \item {Establishing the roadmap and vision of platform architecture, tooling and engineering practices.}
        % \item {Conducting effective one-on-one meetings with team members.}
        \item {Evangelized the concepts of Site Reliability Engineering (SRE) and Service Levels (SLI, SLO, SLA).}
      \end{cvitems}
    }

  \cventry
    {Staff Software Developer (DevOps)} % Job title
    {AppDirect} % Organization
    {Montréal, Canada} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evolved and contributed to open-source Kubernetes network infrastructure projects; API Gateway (Ambassador, Envoy) and ingress-controller.}
        \item {Automated the continuous integration and continuous deployment pipelines of applications; GitOps (Github, Jenkins-dsl, Kubernetes).}
      \end{cvitems}
    }

  \cventry
    {Senior Software Developer (DevOps)} % Job title
    {AppDirect} % Organization
    {Montréal, Canada} % Location
    {2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Application management infrastructure setup and maintenance (Kubernetes, Docker, Terraform, Packer, AWS).}
        \item {Conceived, developed and maintained a self-service development environment provisioning web application (node.js, AngularJS, Terraform, AWS).}
        % \item {Support quality assurance practices by automating and centralizing end-to-end integration testing (AngularJS, Docker-compose, Jenkins).}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {Solutions Médias 360} % Organization
    {Montréal, Canada} % Location
    {2012 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a scalable and redundant architecture of web services and APIs (Java, JAXRS, MySQL, Redis, ElasticSearch).}
        \item {Infrastructure setup and maintenance, "devops" (AWS, Linux, Nginx, HAProxy, monitoring, security).}
        \item {Created and evolved a web-based management tool (AngularJS, node.js).}
        \item {Automated information retrieval and syndication with our industry partners (Java, Spring).}
        % \item {Built and maintained developer tools and environments (Vagrant, CI, Git).}
      \end{cvitems}
    }

%  \cventry
%    {Intermediate Software Developer} % Job title
%    {iWeb Technologies} % Organization
%    {Montréal, Canada} % Location
%    {2011 - 2012} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Developed a software architecture for the delivery of virtual machines in a cloud infrastructure (Agile, TDD).}
%        \item {Programmed REST and JMS web services (Spring, ActiveMQ, CXF).}
%        \item {Interfaced with billing and security APIs (REST).}
%        % \item {Maintained, tested and migrated applications from legacy systems to new technologies (PHP, SOAP, Java).}
%      \end{cvitems}
%    }

%  \cventry
%    {Software Developer} % Job title
%    {Motricity} % Organization
%    {Montréal, Canada} % Location
%    {2009 - 2011, internship and employment} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Developed and programmed REST web services (Java, Tomcat, Spring, Jersey) for a content management and content delivery application for mobile devices.}
%        \item {Developed and maintained a billing and payment platform by SMS (Java, SOAP, Diameter).}
%        \item {Analyzed and modified existing data models (Oracle, MySQL, Hibernate).}
%      \end{cvitems}
%    }

%  \cventry
%    {Semantic Intelligence Programmer} % Job title
%    {Nstein Technologies Inc.} % Organization
%    {Montréal, Canada} % Location
%    {Fall 2008, internship} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Created tools for text normalization in preparation for semantic analysis (Java).}
%        \item {Developed and programmed JSON web services for the administration of a news aggregation portal (Java, Tomcat, MySQL, Hibernate).}
%        \item {Analyzed and programmed a web portal prototype for syndication and visualization of web content (PHP, CSS, AJAX).}
%        \item {Explored and tested the exportation of content on many widget platforms (UWA).}
%      \end{cvitems}
%    }

\end{cventries}