\cvsection{Publications et allocutions}

\cvsubsection{Blogues et articles}

\begin{cvhonors}


  \cvhonor
    {Blogue personnel et articles techniques} % Title
    {Distribué via syndication de contenu sur diverses plateformes, notamment ITNEXT et JaegerTracing } % Event
    {https://alex-gervais.medium.com/} % Link
    {medium.com} % Location
    {2020 à ce jour} % Date(s)

  \cvhonor
    {Reducing the Cognitive Load Associated with Observability} % Title
    {} % Event
    {https://thenewstack.io/reducing-the-cognitive-load-associated-with-observability/} % Link
    {thenewstack.io} % Location
    {Mars 2023} % Date(s)

  \cvhonor
    {Supporting the Evolving Ingress Specification in Kubernetes 1.18} % Title
    {} % Event
    {https://kubernetes.io/blog/2020/06/05/supporting-the-evolving-ingress-specification-in-kubernetes-1.18/} % Link
    {kubernetes.io} % Location
    {Juin 2020} % Date(s)

  \cvhonor
    {AppDirect Case Study - Kubernetes} % Title
    {} % Event
    {https://kubernetes.io/case-studies/appdirect/} % Link
    {kubernetes.io} % Location
    {Mars 2019} % Date(s)

  \cvhonor
    {Fireside Chat with Alex Gervais: Accelerating AppDirect Developer Workflow with Ambassador} % Title
    {} % Event
    {https://blog.getambassador.io/fireside-chat-with-alex-gervais-accelerating-appdirect-developer-workflow-with-ambassador-7586597b1c34} % Link
    {Daniel Bryant; getambassador.io} % Location
    {Sept. 2018} % Date(s)

  \cvhonor
    {Evolution of the AppDirect Kubernetes Network Infrastructure} % Title
    {} % Event
    {https://www.appdirect.com/blog/evolution-of-the-appdirect-kubernetes-network-infrastructure} % Event
    {appdirect.com} % Location
    {Juin 2018} % Date(s)

\end{cvhonors}

\cvsubsection{Conférences et groupes d'utilisateurs}

\begin{cvhonors}

  \cvhonor
    {Running and Extending Keycloak for Your Identity Needs} % Title
    {ConFoo 2022 \& alldaydevops} % Event
    {} % Link
    {Montréal \& En ligne} % Location
    {Fev. \& Nov. 2022} % Date(s)

  \cvhonor
    {Build Your Own Serverless With Knative} % Title
    {ConFoo 2020 \& alldaydevops} % Event
    {} % Link
    {Montréal \& En ligne} % Location
    {Fev. \& Nov. 2020} % Date(s)

  \cvhonor
    {From Grief to Growth: The 7 Stages of Observability} % Title
    {ConFoo 2020} % Event
    {} % Link
    {Montréal} % Location
    {Fev. 2020} % Date(s)

  \cvhonor
    {GitOps in Practice} % Title
    {devopsdays Montréal} % Event
    {} % Link
    {Montréal} % Location
    {Nov. 2019} % Date(s)

  \cvhonor
    {The Evolution of the AppDirect Kubernetes Network Infrastructure} % Title
    {KubeCon + CNCFCon North America 2018} % Event
    {} % Link
    {Seattle} % Location
    {Déc. 2018} % Date(s)

  \cvhonor
    {Étouffez-vous? — Un cas d’API Gateway} % Title
    {devopsdays Montréal} % Event
    {} % Link
    {Montréal} % Location
    {Oct. 2018} % Date(s)

  \cvhonor
    {AppDirect+GitHub since 2010} % Title
    {Montréal GitHub Meetup} % Event
    {} % Link
    {Shopify Montréal} % Location
    {Oct. 2017} % Date(s)

  \cvhonor
    {HA Kubernetes Deployment} % Title
    {Meetup \#2 - User stories, Kubernetes-Montréal} % Event
    {} % Link
    {CloudOps Montréal} % Location
    {Oct. 2016} % Date(s)

\end{cvhonors}